---
title: "CodeBook"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Variable List and Descriptions
**Variable Name** | **Description**
------------------|-----------------------------------------------
subject	ID        |the subject who performed the activity for each window sample. Its range is from 1 to 30.
activity          |Activity name
featDomain	      |Feature: Time domain signal or frequency domain signal (Time or Freq)
featInstrument    |Feature: Measuring instrument (Accelerometer or Gyroscope)
featAcceleration  |Feature: Acceleration signal (Body or Gravity)
featVariable      |Feature: Variable (Mean or SD)
featJerk	        |Feature: Jerk signal
featMagnitude	    |Feature: Magnitude of the signals calculated using the Euclidean norm
featAxis	        |Feature: 3-axial signals in the X, Y and Z directions (X, Y, or Z)
featCount	        |Feature: Count of data points used to compute average
featAverage	      |Feature: Average of each variable for each activity and each subject

# Tidy Data set Structure
```{r}
str(TidyDataSet)
```

# List of the key variables in the Tidy data set
```{r}
names(TidyDataSet)
```

# Showing a few rows of the Tidy data set
```{r}
head(TidyDataSet)
```

# Summary of the variables in the Tidy data set
```{r}
summary(TidyDataSet)
```

# List all possible combinations of features
```{r}
TidyDataSet[, .N, by=c(names(TidyDataSet)[grep("^feat", names(TidyDataSet))])]
```

# Saving to a file for submission
```{r}
f <- file.path(path, "TidyDataSet.txt")
write.table(TidyDataSet, f, quote=FALSE, sep="\t", row.names=FALSE)
```

# knitting Codebook
```{r}
require(knitr)
knit("Codebook.Rmd", output="codebook.md", encoding="ISO8859-1", quiet=TRUE)
```

# Creating HTML code book
```{r}
require(markdown)
markdownToHTML("codebook.md", "codebook.html")
```